Conversations in time: interactive visualisation to explore structured temporal data

### 2020-08-12 tsibbletalk.Rmd
minor tweak
added a bit detailed description to figure 1

Figure \ref{fig:highlight-retail} highlights not only a series with strongest seasonality, but also a need to querying interesting series on the fly. The two plots are static, but can be considered as linked views via the common `key` variables between two tables. This motivates enabling interactivity of `tsibble` and `tsibble`-derived objects for exploratory data analysis in a lightning manner.

>>>>

Figure \ref{fig:highlight-retail} highlights not only a series with strongest seasonality, but also a need to querying interesting series on the go. Without interactivity, one needs to first filter the interesting series out from the features table, and join back to the original `tsibble` in order to examine its trend in relation to others. This procedure can soon grow cumbersome if many series to be discovered. Despite that the two plots are static, they can be considered as linked views via the common `key` variables between two tables. This motivates enabling interactivity of `tsibble` and `tsibble`-derived objects for rapid exploratory data analysis.

### 2020-08-12 tsibbletalk.tex
minor tweak
added a bit detailed description to figure 1

Figure \ref{fig:highlight-retail} highlights not only a series with
strongest seasonality, but also a need to querying interesting series on
the fly. The two plots are static, but can be considered as linked views
via the common \texttt{key} variables between two tables. This motivates
enabling interactivity of \texttt{tsibble} and \texttt{tsibble}-derived
objects for exploratory data analysis in a lightning manner.

>>>>

Figure \ref{fig:highlight-retail} highlights not only a series with
strongest seasonality, but also a need to querying interesting series on
the go. Without interactivity, one needs to first filter the interesting
series out from the features table, and join back to the original
\texttt{tsibble} in order to examine its trend in relation to others.
This procedure can soon grow cumbersome if many series to be discovered.
Despite that the two plots are static, they can be considered as linked
views via the common \texttt{key} variables between two tables. This
motivates enabling interactivity of \texttt{tsibble} and
\texttt{tsibble}-derived objects for rapid exploratory data analysis.
